A North Sámi to South Sámi machine translation prototype

### 2014-02-09 paper/paper.tex
update
About the sme analyser, and two possible refs for sma, on for the socioling situation. Make a motivation section?

@@

@@

@@

\subsection{Qualitative}
%@lene

From the oovtast-presentation:
\begin{table*} 
\begin{center}
\begin{tabular}{|l|r||r|r|r|}
\hline
\textbf{ }  & \textbf{MT} &  \textbf{A} & \textbf{B} & \textbf{C} \\
\hline
Lexical differences: & &   37 & 27 & 19 \\
\hline
Morphological differences: & &   15 & 14 & 16 \\
\hline
\hline
\multicolumn{5}{|l|} {\textbf{Syntax} }   \\
\hline
SOV/SAdvlV & 4 &  10 & 12 & 12 \\
\hline
Det pronomen & 4 &   7 & 4 & 7 \\
\hline
Ind. articles & 0 &   7 & 0 & 1 \\
\hline
Complement instead of genitive mod. & -- &   2 & 2 & 0 \\
\hline
Habitive \textit{utnedh} & 0 &  5 & 2 & 2 \\
\hline
\hline
All together & 8 &   31 & 20 & 21 \\
\hline
\end{tabular}
\end{center}
\end{table*}

>>>>

\section{Motivation}
sma sociolinguistic situation \cite{Todalsvahken2007}

@@

The North Saami analyser has an F-score of 0.93 for morphological disambiguation
and assignment fof grammatical functions \cite{AntonsenEtalReusing2010}.

@@

Here is some facts about the South Saami analyser, if we need it \cite{smadis2011}.

@@

\subsection{Qualitative}
%@lene
\subsubsection{Lexicon}
The Norwegian text consisted of 288 words. The three evaluators had chosen respectively 42, 30 and 23 other words than the mt-system, for only for 9 words all the evaluators had chosen another word.

\subsubsection{Morphology}

\subsubsection{Syntax}

From the oovtast-presentation:
\begin{table*}[h] 
\begin{center}
\begin{tabular}{|l|r||r|r|r|}
\hline
\textbf{ }  & \textbf{MT} &  \textbf{A} & \textbf{B} & \textbf{C} \\
\hline
Lexical differences: & &   42 & 30 & 23 \\
\hline
Morphological differences: & &   7 & 7 & 6 \\
\hline
\hline
\multicolumn{5}{|l|} {\textbf{Syntax} }   \\
\hline
SOV/SAdvlV & 4 &  10 & 12 & 12 \\
\hline
Det pronomen & 4 &   7 & 4 & 7 \\
\hline
Ind. articles & 0 &   7 & 0 & 1 \\
\hline
Complement instead of genitive mod. & -- &   2 & 2 & 0 \\
\hline
Habitive \textit{utnedh} & 0 &  5 & 2 & 2 \\
\hline
\hline
\end{tabular}
\end{center}
\label{table:qualitative}
\caption{A break down of translation errors.}
\end{table*}
